### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
added table

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure", "all")
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````
